Improved state-space models for inference about spatial and temporal variation in abundance from count data

### 2013-11-12 Dail_Mad_ext.tex
to results

We simulated data for 100 sites over 40 years.  All
simulations assumed initial abundance was Poisson distributed
and no covariates affected initial abundance, dynamics, or
detection probability.  Our first series of simulations
assumed dynamics were exponential.  We ran 1000 simulations for
each combination of low, medium, and high $\Lambda \in
\{1,5,10\}$, $r \in \{-0.005, 0, 0.005\}$, and
$p \in \{0.05, 0.25, 0.5\}$. % (Table 1; 27 total combinations).
Our second series of simulations changed dynamics to the Ricker-logistic
model. We used an initial abundance of 10 and a detection probability
of 0.25, and simulated low, medium, and high values of equilibrium
abundance and maximum growth rate, each with 1000 simulations (Table 1;
9 total combinations). Our third series of simulations was based
on the Ricker-logistic + immigration dynamics model; here we fixed all
parameters the same as the Ricker-logistic model (with r = 0.05 and K = 10) and
simulated low, medium, and high values of immigration rate with 1000
simulation each (Table 1).

>>>>

We simulated data for 100 sites over 40 years.  All
simulations assumed initial abundance was Poisson distributed
and no covariates affected initial abundance, dynamics, or
detection probability.  Our first series of simulations
assumed dynamics were exponential.  We ran 1000 simulations for
each combination of low, medium, and high $\Lambda \in
\{1,5,10\}$, $r \in \{-0.005, 0, 0.005\}$, and
$p \in \{0.05, 0.25, 0.5\}$. % (Table 1; 27 total combinations).
Our second series of simulations changed dynamics to the Ricker-logistic
model. We used an initial abundance of 10 and a detection probability
of 0.25, and simulated low, medium, and high values of equilibrium
abundance and maximum growth rate, each with 1000 simulations (Table 1;
9 total combinations). Our third series of simulations was based
on the Ricker-logistic + immigration dynamics model; here we fixed all
parameters the same as the Ricker-logistic model (with $r$ = 0.05 and $K$ = 10) and
simulated low, medium, and high values of immigration rate with 1000
simulation each (Table 1).
